\texttt{SuperScreen}: An open-source package for simulating the magnetic response of 2D superconductors

### 2021-07-30 main_cpc.tex
Add iamges

\subsection{Screening}
\label{section:example:screening}

\subsection{Inductance}
\label{section:examples:inductance}

>>>>

\subsection{Screening: superconducting disk}
\label{section:example:screening}

\begin{figure}
    \centering
    \includegraphics[scale=.40]{examples/images/disk/disk_uniform_field.png}
    \caption{Caption}
    \label{fig:disk_uniform_field}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.40]{examples/images/ring/ring_uniform_field.png}
    \caption{Caption}
    \label{fig:ring_uniform_field}
\end{figure}

\subsection{Inductance: superconducting ring}
\label{section:examples:inductance}

\begin{figure}
    \centering
    \includegraphics[scale=.40]{examples/images/ring/ring_circulating_current.png}
    \caption{Caption}
    \label{fig:ring_circ_current}
\end{figure}

\begin{figure}
    \centering
    \includegraphics[scale=.40]{examples/images/ring/square_ring_circulating_current.png}
    \caption{Caption}
    \label{fig:square_ring_circ_current}
\end{figure}
